---
title: "R Notebook"
output: html_notebook
---
This normalized the percentages given into numeric decimals.
```{r}
flavors_of_cacao$`Cocoa Percent` = as.numeric(sub("%","",flavors_of_cacao$`Cocoa Percent`))/100

```
Below we can see that at least the cocoa percentage data is normally distributed
```{r}
hist(flavors_of_cacao$`Cocoa
Percent`, xlab="Cocoa Percentage", main = "Cocoa Percentage over all Data")
```

And the rating is skewed left with what could be interpreted as a normal distribution
```{r}
hist(flavors_of_cacao$Rating, xlab="Ratings", main="Rating distribution over all data")
```


As can be seen in this plot, there is not a simple correlation between cocoa percentage and the rating.

```{r}
plot(flavors_of_cacao$`Cocoa
Percent`, flavors_of_cacao$Rating, xlab="Cocoa Percentage", ylab="Rating", main = "All Data")
```

We could possibly hone in on company/location specific characteristics though. Here it could be argued that midrange cocoa percentages fair better than their extremes?
```{r}
subSwiss = subset(flavors_of_cacao, flavors_of_cacao$`Company
Location` == "Switzerland")
plot(subSwiss$`Cocoa
Percent`, subSwiss$Rating, xlab="Cocao Percentage", ylab="Rating", main ="Swiss Based Chocolate Companies")

hist(subSwiss$`Cocoa
Percent`, weight)
```

```{r}

```

